---
title: "Improvised plots Wheat DE"
author: "Lokesh"
date: "`r paste0('<b>Lokesh Mano</b> • ',format(Sys.time(), '%d-%b-%Y'))`"
output: 
  rmarkdown::html_document:
    code_folding: 'hide'
    toc: true
    toc_float: true
    smart: true
    number_sections: true
    highlight: tango
    self_contained: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r wrap-hook, include=FALSE}
# Ignore this part! This is only for formatting this document in the html file!
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

# Overall 

## Overview

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(pheatmap)
library(ggpubr)
library(dplyr)
library(tidyverse)
library(ComplexHeatmap)
library(treemapify)

load("wheat_de1.RData")
silva_hits <- read.table("Trinity_ass_200_vs_Sil132DB_all_NEW.hits")

ws_t1_annot <- de_ws_t1 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "Straw", "Control")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ws_t1_annot$enz_class <- factor(ws_t1_annot$enz_class)
ws_t1_annot$enz_family <- factor(ws_t1_annot$enz_family)
#ggplot(ws_all_annot) + geom_bar(aes(x = condition, fill = enz_class), stat = "count")

ovr_plot_t1 <- ws_t1_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t1$test <- "Straw-T1"

ws_t3_annot <- de_ws_t3 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "Straw", "Control")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ovr_plot_t3 <- ws_t3_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t3$test <- "Straw-T3"

ws_t6_annot <- de_ws_t6 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "Straw", "Control")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ovr_plot_t6 <- ws_t6_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t6$test <- "Straw-T6"

ws_t6vt1_annot <- de_ws_t6vt1 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "T6", "T1")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ovr_plot_t6vt1_ws <- ws_t6vt1_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t6vt1_ws$test <- "T6vT1-Straw"

ws_t6vt3_annot <- de_ws_t6vt3 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "T6", "T3")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ovr_plot_t6vt3_ws <- ws_t6vt3_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t6vt3_ws$test <- "T6vT3-Straw"

wc_t6vt3_annot <- de_wc_t6vt3 %>% 
  mutate(abs_fc = abs(log2FoldChange))%>%
  mutate(condition = ifelse(log2FoldChange > 0, "T6", "T3")) %>%
  mutate(direction = ifelse(log2FoldChange > 0, "Positive", "Negative")) %>%
  rownames_to_column("Transcript") %>% 
  left_join(tdb_annot %>% rownames_to_column("Transcript"), by = "Transcript") %>%
  left_join(taxa_annot %>% rownames_to_column("Transcript"), by = "Transcript") 

ovr_plot_t6vt3_wc <- wc_t6vt3_annot %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  group_by(condition, direction) %>%
  summarise(num_sig= n(), sum_mean = sum(baseMean), sum_FC = sum(log2FoldChange))
ovr_plot_t6vt3_wc$test <- "T6vT3-Control"

ovr_nsig_data <- rbind(ovr_plot_t1, ovr_plot_t3, ovr_plot_t6, ovr_plot_t6vt1_ws, ovr_plot_t6vt3_ws, ovr_plot_t6vt3_wc)

ovr_nsig_data <- ovr_nsig_data %>%
  mutate(Main_test = ifelse(any(grepl("Straw-", test)), "Straw", "Time"))

ovr_nsig_data$condition <- factor(ovr_nsig_data$condition, levels = c("Control", "Straw", "T1", "T3", "T6"))
  
ggplot(data = ovr_nsig_data) +
  geom_bar(aes(x = test, y = log10(num_sig), fill = condition),
           position = "dodge",stat = "identity") +
  geom_text(aes(test, log10(num_sig), label=num_sig, group = condition),
            vjust = 1.5, size=4, position = position_dodge(width = .9)) +
  facet_wrap(~Main_test, scales = "free_x") +
  scale_fill_manual(values = c("#F5B041", "#6C3483", "#D5D8DC", "#808B96", "#2C3E50")) +
  ylab("Number of significant transcripts") +
  theme_pubclean(base_size = 12) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank())
  
  
```

## Effect of Straw in T1

```{r, message=FALSE, warning=FALSE}
ws_t1_tdb <- ws_t1 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(enz_class, enz_family) %>%
  summarise(num_sig= n(), mean_log2FC = mean(abs(log2FoldChange))) %>%
  filter(!is.na(enz_class)) %>%
  arrange(desc(num_sig))

ggplot(data = ws_t1_tdb, aes(fill = mean_log2FC, area = num_sig, label= enz_family, subgroup=enz_class)) +
  geom_treemap() +
  geom_treemap_text(colour ="white", place = "centre") +
  theme_pubclean(base_size = 12) +
  scale_fill_gradient(low = "#A9CCE3", high = "#1B4F72")
```

There were `380` transcripts in total that were significantly abundant in straw compared to control at T1! Out of which `306` had matchesto the TDB. The top CAZy families are listed below:

```{r, message=FALSE, warning=FALSE}
#ws_all %>% 
#  filter(condition == "Straw") %>%
#  dim()
#sum(ws_all_tdb$num_sig)
kable(head(ws_t1_tdb, 10))
```

### Heatmap of COG

```{r, message=FALSE, warning=FALSE}
tmm_mat <- read.table("SeqCap_gene.TMM.EXPR.matrix", header = T, row.names = 1, check.names = F)
sample_meta <-  read.table("All.samples", header = T, check.names = F)
sm_w_t1 <- sample_meta %>% 
  filter(Time == "T1") %>% 
  filter(Manag == "W") %>%
  arrange(Straw)

  
ws_t1_egg <- ws_t1 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(!is.na(cog_lev1))
ws_t1_tmm_egg <- tmm_mat[ws_t1_egg$Transcript, (colnames(tmm_mat) %in% sm_w_t1$Samples)]

ws_t1_tmm_egg_cog_lev2 <- ws_t1_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t1_egg, by = "Transcript") %>% 
  group_by(Sample_ID, cog_lev2) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)
temp <- ws_t1_tmm_egg_cog_lev2$cog_lev2
ws_t1_tmm_egg_cog_lev2$cog_lev2 <- NULL
row.names(ws_t1_tmm_egg_cog_lev2) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t1_tmm_egg_cog_lev2, border_color=NA, annotation_col=sm_w_t1[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = F, cluster_cols = F)

```

```{r, message=FALSE, warning=FALSE}
ws_t1_tmm_egg_cog_enz <- ws_t1_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t1_egg, by = "Transcript") %>% 
  filter(cog_lev2 == "Carbohydrate transport and metabolism") %>%
  group_by(Sample_ID, cog_enzid) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)

temp <- ws_t1_tmm_egg_cog_enz$cog_enzid
ws_t1_tmm_egg_cog_enz$cog_enzid <- NULL
row.names(ws_t1_tmm_egg_cog_enz) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t1_tmm_egg_cog_enz, border_color=NA, annotation_col=sm_w_t1[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = F, cluster_cols = F)
```


## Effect of Straw in T3

```{r, message=FALSE, warning=FALSE}
ws_t3_tdb <- ws_t3 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(enz_class, enz_family) %>%
  summarise(num_sig= n(), mean_log2FC = mean(abs(log2FoldChange))) %>%
  filter(!is.na(enz_class)) %>%
  arrange(desc(num_sig))

ggplot(data = ws_t3_tdb, aes(fill = mean_log2FC, area = num_sig, label= enz_family, subgroup=enz_class)) +
  geom_treemap() +
  geom_treemap_text(colour ="white", place = "centre") +
  theme_pubclean(base_size = 12) +
  scale_fill_gradient(low = "#A9CCE3", high = "#1B4F72")
```

There were `361` transcripts in total that were significantly abundant in straw compared to control at t3! Out of which `303` had matches to the TDB. The top CAZy families are listed below:

```{r, message=FALSE, warning=FALSE}
#ws_all %>% 
#  filter(condition == "Straw") %>%
#  dim()
#sum(ws_all_tdb$num_sig)
kable(head(ws_t3_tdb, 10))
```

### Heatmap of COG

```{r, message=FALSE, warning=FALSE}
#tmm_mat <- read.table("SeqCap_gene.TMM.EXPR.matrix", header = T, row.names = 1, check.names = F)
#sample_meta <-  read.table("All.samples", header = T, check.names = F)
sm_w_t3 <- sample_meta %>% 
  filter(Time == "T3") %>% 
  filter(Manag == "W") %>%
  arrange(Straw)

  
ws_t3_egg <- ws_t3 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(!is.na(cog_lev1))
ws_t3_tmm_egg <- tmm_mat[ws_t3_egg$Transcript, (colnames(tmm_mat) %in% sm_w_t3$Samples)]

ws_t3_tmm_egg_cog_lev2 <- ws_t3_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t3_egg, by = "Transcript") %>% 
  group_by(Sample_ID, cog_lev2) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)
temp <- ws_t3_tmm_egg_cog_lev2$cog_lev2
ws_t3_tmm_egg_cog_lev2$cog_lev2 <- NULL
row.names(ws_t3_tmm_egg_cog_lev2) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t3_tmm_egg_cog_lev2, border_color=NA, annotation_col=sm_w_t3[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = F, cluster_cols = F)

```

```{r, message=FALSE, warning=FALSE}
ws_t3_tmm_egg_cog_enz <- ws_t3_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t3_egg, by = "Transcript") %>% 
  filter(cog_lev2 == "Carbohydrate transport and metabolism") %>%
  group_by(Sample_ID, cog_enzid) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)

temp <- ws_t3_tmm_egg_cog_enz$cog_enzid
ws_t3_tmm_egg_cog_enz$cog_enzid <- NULL
row.names(ws_t3_tmm_egg_cog_enz) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t3_tmm_egg_cog_enz, border_color=NA, annotation_col=sm_w_t3[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = T, cluster_cols = F)
```

## Effect of Straw in T6

```{r, message=FALSE, warning=FALSE}
ws_t6_tdb <- ws_t6 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(enz_class, enz_family) %>%
  summarise(num_sig= n(), mean_log2FC = mean(abs(log2FoldChange))) %>%
  filter(!is.na(enz_class)) %>%
  arrange(desc(num_sig))

ggplot(data = ws_t6_tdb, aes(fill = mean_log2FC, area = num_sig, label= enz_family, subgroup=enz_class)) +
  geom_treemap() +
  geom_treemap_text(colour ="white", place = "centre") +
  theme_pubclean(base_size = 12) +
  scale_fill_gradient(low = "#A9CCE3", high = "#1B4F72")
```

There were `286` transcripts in total that were significantly abundant in straw compared to control at t6! Out of which `219` had matches to the TDB. The top CAZy families are listed below:

```{r, message=FALSE, warning=FALSE}
#ws_all %>% 
#  filter(condition == "Straw") %>%
#  dim()
#sum(ws_all_tdb$num_sig)
kable(head(ws_t6_tdb, 10))
```

### Heatmap of COG

```{r, message=FALSE, warning=FALSE}
#tmm_mat <- read.table("SeqCap_gene.TMM.EXPR.matrix", header = T, row.names = 1, check.names = F)
#sample_meta <-  read.table("All.samples", header = T, check.names = F)
sm_w_t6 <- sample_meta %>% 
  filter(Time == "T6") %>% 
  filter(Manag == "W") %>%
  arrange(Straw)

  
ws_t6_egg <- ws_t6 %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(!is.na(cog_lev1))
ws_t6_tmm_egg <- tmm_mat[ws_t6_egg$Transcript, (colnames(tmm_mat) %in% sm_w_t6$Samples)]

ws_t6_tmm_egg_cog_lev2 <- ws_t6_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t6_egg, by = "Transcript") %>% 
  group_by(Sample_ID, cog_lev2) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)
temp <- ws_t6_tmm_egg_cog_lev2$cog_lev2
ws_t6_tmm_egg_cog_lev2$cog_lev2 <- NULL
row.names(ws_t6_tmm_egg_cog_lev2) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t6_tmm_egg_cog_lev2, border_color=NA, annotation_col=sm_w_t6[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = F, cluster_cols = F)

```

```{r, message=FALSE, warning=FALSE}
ws_t6_tmm_egg_cog_enz <- ws_t6_tmm_egg %>%
  rownames_to_column(var = "Transcript") %>%
  gather(Sample_ID, count, -Transcript) %>% 
  left_join(ws_t6_egg, by = "Transcript") %>% 
  filter(cog_lev2 == "Carbohydrate transport and metabolism") %>%
  group_by(Sample_ID, cog_enzid) %>%
  summarise(sum_count = sum(count)) %>%
  spread(Sample_ID, sum_count)

temp <- ws_t6_tmm_egg_cog_enz$cog_enzid
ws_t6_tmm_egg_cog_enz$cog_enzid <- NULL
row.names(ws_t6_tmm_egg_cog_enz) <- temp

my_colour = list(
     Straw = c(C = "#F5B041", S = "#6C3483")
)

pheatmap(ws_t6_tmm_egg_cog_enz, border_color=NA, annotation_col=sm_w_t6[,c("Straw"),drop=F],annotation_legend=T, scale = "row", annotation_colors = my_colour, show_colnames = T, cluster_cols = F)
```

## Taxonomy in Straw at different times

Here I try to make the taxonomy plot by combining the taxonomies that are significantly different in the 3 time points while comparing straw samples to the control! 

```{r, message=FALSE, warning=FALSE}
ws_t1_taxa <- ws_t1 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Kingdom, Phylum) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t1_taxa$time <- "T1"

ws_t3_taxa <- ws_t3 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Kingdom, Phylum) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t3_taxa$time <- "T3"

ws_t6_taxa <- ws_t6 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Kingdom, Phylum) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t6_taxa$time <- "T6"

ws_taxa_allT <- rbind(ws_t1_taxa, ws_t3_taxa, ws_t6_taxa)
ws_taxa_allT$Kingdom <- factor(ws_taxa_allT$Kingdom, levels = c("Bacteria", "Eukaryota", "unknown"))

rem_phyla <- ws_taxa_allT %>% 
  group_by(Phylum) %>%
  summarise(tot_sig= sum(num_sig)) %>%
  filter(tot_sig > 5)

ws_taxa_allT <- ws_taxa_allT %>% 
  filter(Phylum %in% rem_phyla$Phylum) 


ggplot(ws_taxa_allT) +
  geom_bar(aes(x = Phylum, y = num_sig, fill = time), 
           stat = "identity", position = position_dodge(preserve = "single")) +
  geom_text(aes(Phylum, num_sig, label=num_sig, group = time), 
            vjust = -0.5, size=4, position = position_dodge(width = .9)) +
  theme_light(base_size = 12) +
  ylab("Number of significant transcripts") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.title = element_blank()) +
  facet_grid(cols = vars(Kingdom), space = "free", scales = "free") +
  scale_fill_manual(values = c("#D5D8DC", "#808B96", "#2C3E50")) 

```

### Important Phyla

```{r, message=FALSE, warning=FALSE}
ws_t1_taxa <- ws_t1 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Phylum, Genus) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t1_taxa$time <- "T1"

ws_t3_taxa <- ws_t3 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Phylum, Genus) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t3_taxa$time <- "T3"

ws_t6_taxa <- ws_t6 %>%
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "Straw") %>%
  group_by(Phylum, Genus) %>%
  filter(!is.na(Phylum)) %>%
  summarise(num_sig= n())
ws_t6_taxa$time <- "T6"

ws_taxa_allT <- rbind(ws_t1_taxa, ws_t3_taxa, ws_t6_taxa)

keep_phyla <- c("Actinobacteria", "Proteobacteria", "Ascomycota")

rem_phyla <- ws_taxa_allT %>% 
  filter(Phylum %in% keep_phyla) %>%
  group_by(Genus) %>%
  summarise(tot_sig= sum(num_sig)) %>%
  filter(tot_sig > 5)

ws_taxa_allT <- ws_taxa_allT %>% 
  filter(Phylum %in% keep_phyla) %>%
  filter(Genus %in% rem_phyla$Genus) 
ws_taxa_allT$Phylum <- factor(ws_taxa_allT$Phylum, levels = c("Actinobacteria", "Proteobacteria", "Ascomycota"))

ggplot(ws_taxa_allT) +
  geom_bar(aes(x = Genus, y = num_sig, fill = time), 
           stat = "identity", position = position_dodge(preserve = "single")) +
  geom_text(aes(Genus, num_sig, label=num_sig, group = time), 
            vjust = -0.5, size=4, position = position_dodge(width = .9)) +
  theme_light(base_size = 12) +
  ylab("Number of significant transcripts") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.title = element_blank()) +
  facet_grid(cols = vars(Phylum), space = "free", scales = "free") +
  scale_fill_manual(values = c("#D5D8DC", "#808B96", "#2C3E50")) 
```

## Change in time (Mainly straw T6 vs T1)

Since this is the most interesting part, let us just focus on this!

### In T6

```{r, message=FALSE, warning=FALSE}
ws_t6vt1_tdb <- ws_t6vt1_all %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "T6") %>%
  group_by(enz_class, enz_family) %>%
  summarise(num_sig= n(), mean_log2FC = mean(abs(log2FoldChange))) %>%
  filter(!is.na(enz_class)) %>%
  arrange(desc(num_sig))

ggplot(data = ws_t6vt1_tdb, aes(fill = mean_log2FC, area = num_sig, label= enz_family, subgroup=enz_class)) +
  geom_treemap() +
  geom_treemap_text(colour ="white", place = "centre") +
  theme_pubclean(base_size = 12) +
  scale_fill_gradient(low = "#A9CCE3", high = "#1B4F72")
```

There were `66` transcripts in total that were significantly abundant t6 compared to t1 in straw samples! Out of which `32` had matches to the TDB. The top CAZy families are listed below:

```{r, message=FALSE, warning=FALSE}
#ws_all %>% 
#  filter(condition == "Straw") %>%
#  dim()
#sum(ws_all_tdb$num_sig)
kable(head(ws_t6vt1_tdb, 10))
```

```{r, message=FALSE, warning=FALSE}
ws_t6vt1_tdb <- ws_t6vt1_all %>% 
  filter(!(is.na(enz_class) & (Transcript %in% silva_hits$V1))) %>%
  filter(condition == "T1") %>%
  group_by(enz_class, enz_family) %>%
  summarise(num_sig= n(), mean_log2FC = mean(abs(log2FoldChange))) %>%
  filter(!is.na(enz_class)) %>%
  arrange(desc(num_sig))

ggplot(data = ws_t6vt1_tdb, aes(fill = mean_log2FC, area = num_sig, label= enz_family, subgroup=enz_class)) +
  geom_treemap() +
  geom_treemap_text(colour ="white", place = "centre") +
  theme_pubclean(base_size = 12) +
  scale_fill_gradient(low = "#A9CCE3", high = "#1B4F72")
```

There were `262` transcripts in total that were significantly abundant t1 compared to t6 in straw samples! Out of which `196` had matches to the TDB. The top CAZy families are listed below:

```{r, message=FALSE, warning=FALSE}
#ws_all %>% 
#  filter(condition == "Straw") %>%
#  dim()
#sum(ws_all_tdb$num_sig)
kable(head(ws_t6vt1_tdb, 10))
```

```{r}
de_wheat_overview <- ggplot(data = ovr_nsig_data) + 
  geom_bar(aes(x = test, y = log10(num_sig), fill = condition),
           position = "dodge",stat = "identity") +
  geom_text(aes(test, log10(num_sig), label=num_sig, group = condition),
            vjust = 1.5, size=4, position = position_dodge(width = .9)) +
  facet_wrap(~Main_test, scales = "free_x") +
  scale_fill_manual(values = c("#F5B041", "#6C3483", "#D5D8DC", "#808B96", "#2C3E50")) +
  ylab("Number of DE transcripts [log10]") +
  theme_pubclean(base_size = 12) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank()) + labs(fill = "") + labs(tag="a)") +
  scale_y_continuous(limits = c(0, 2.6))
```
